Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-17 manuscript.Rmd
update manuscript (remove bib loading, add grant)

author_note: >
  We would like to thank Courtney Soderberg for creating the first version of the TOST function to test two independent proportions.
  DL: Article conceptualization, programming TOSTER package and spreadsheet, main contributor to the introduction section and, discussion section.
  AS and PI: Main contributors to examples and figures.
  All authors contributed to manuscript conceptualization, editing, review for submission, and additional software development. AS and PI contributed equally to the manuscript, and order was determined by executing the following commands in R:
  \newline
  `set.seed(7998976/5271)`
  \newline
  `x <- sample(c("Anne", "Peder"), 1)`
  \newline
  `print(paste("The winner is", x, "!"))`
  \newline

@@

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---
getwd()
```{r include = FALSE}
library("papaja")

# papaja:::fetch_zotero_refs(
#   x = "1786197"
#   , bib_name = "equivalence.bib"
#   , API_key = "F7JGNtCxZGT6q87Eeg2zNWiP"
#   , lib_type = "group"
# )
```

>>>>

author_note: >
  This work was funded by VIDI grant 452-17-013. We would like to thank Courtney Soderberg for creating the first version of the TOST function to test two independent proportions. Authorship contributions: 
  DL: Article conceptualization, programming TOSTER package and spreadsheet, main contributor to the introduction section and, discussion section.
  AS and PI: Main contributors to examples and figures.
  All authors contributed to manuscript conceptualization, editing, review for submission, and additional software development. AS and PI contributed equally to the manuscript, and order was determined by executing the following commands in R:
  \newline
  `set.seed(7998976/5271)`
  \newline
  `x <- sample(c("Anne", "Peder"), 1)`
  \newline
  `print(paste("The winner is", x, "!"))`
  \newline

@@

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---
getwd()
```{r include = FALSE}
library("papaja")
```
